An exact method for the multi-product p-batch processing time maximization problem

### 2023-10-16 manuscript/manuscript.tex
updating paper - abstract

\begin{abstract} 
The multi-product batch (MPB) problems have been widely studied by the researchers. Among the most complex MPB problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines. When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound products considering that the products that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch. Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing problem.

In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present the multi-product batch processing time maximization (MBPTM) problem. We also present a mathematical model for the MBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

>>>>

\begin{abstract} 
The multi-product batch (MPB) problems have been widely studied by the researchers. Among the most complex MPB problems are the multi-product p-batch scheduling (MPPBS) problems, where jobs must be scheduled on parallel batch processing machines. When applying some local search heuristics to solve a MPPBS problem, it can be necessary to determine, in each iteration, the maximum processing time for batches of compound jobs considering that the jobs that make up the batches have different processing rates, and that there are limitations for the amount produced for each product, as well as for the set of products of the compound  batch. Using the denominations present in the literature, this sub-problem can be simply referred as a single stage multi-product p-batch sizing (SSMPPBS) problem . Once a SSMPPBS problem needs to be solved in each iteration, the efficiency of the method developed for solving a SSMPPBS problem has a huge impact on the computational cost of the local search algorithm. In addition, for some industries, efficiently solving an SSMPPBS problem can have a significant impact on storage costs and customer satisfaction. In this paper we presente a mathematical model and an exact method with polynomial time complexity for the SSMPPBS problem. We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method. We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large. As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances. 
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}
